FinalManuscript_DISCS_UG

### 2019-04-30 parts/00_abstract.tex
More revisions

\begin{thesisabstract}
    \noindent
    Homomorphic cryptography allows for encrypted data to be modified and operated on without requiring decryption, although current homomorphic cryptosystems are either limited in their permitted operations or are significantly more time-intensive than standard non-homomorphic cryptosystems. Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy. In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), Dijk--Gentry--Halevi--Vaikuntanathan (DGHV), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy. Furthermore, as an extension to previous research, we attempt to support non-linear image processing operations by deriving and implementing applicable closed-form approximations. Preliminary results have shown that the Paillier and DGK cryptosystems are comparable in accuracy and may be used for image negation, but only the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.

>>>>

\begin{thesisabstract}
    \noindent
    Homomorphic cryptography allows for encrypted data to be modified and operated on without requiring decryption, although current homomorphic cryptosystems are either limited in their permitted operations or are significantly more time-intensive than standard non-homomorphic cryptosystems. Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy. We compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), Dijk--Gentry--Halevi--Vaikuntanathan (DGHV), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications by implementing a software library equipped with these cryptosystems and comparing their time efficiency and accuracy. We attempt to support non-linear image processing operations by deriving and implementing applicable closed-form approximations. Results have shown that the Paillier and DGK cryptosystems are comparable in accuracy and may be used for image negation, but only the Paillier cryptosystem is consistent enough to produce reasonable to accurate results for logarithm intensity transformation. The DGHV and BGV cryptosystems are significantly slower and are not applicable for practical use.

### 2019-04-30 parts/01_introduction_01contextofstudy.tex
More revisions

Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}. Various cryptosystems have been developed, which allow for the secure transmission of data using encryption and decryption schemes~\cite{bauer_cryptosystem_2005}.

One particular application of cryptography is image encryption. While cryptosystems used to encrypt general digital data, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images~\cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed~\cite{murugan_survey_2018}.

 Using a homomorphic cryptosystem, operations can be performed on encrypted data while keeping both the operands and resulting value secure. The result of the operations can be recovered when the data is decrypted. In this manner, data is manipulated without compromising data privacy~\cite{fontaine_survey_2007, sen_homomorphic_2013}. There is additional interest in being able to perform image manipulation operations on encrypted images such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}. More advanced operations have also been implemented using homomorphic cryptosystems, such as facial recognition \cite{hutchison_privacy-preserving_2009} and neural networks \cite{hesamifard_cryptodl:_2017}. While secure linear image operations have been implemented \cite{ziad_cryptoimg:_2016}, preprocessing which requires non-linear operations, such as certain methods of illumination processing \cite{oravec_illumination_2010}, has yet to be performed in the encrypted domain. This study in particular focuses on facial recognition.

>>>>

Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}. Various cryptosystems have been developed which allow for the secure transmission of data using encryption and decryption schemes~\cite{bauer_cryptosystem_2005}.

One particular application of cryptography is image encryption. While cryptosystems used to encrypt general digital data, such as the Advanced Encryption Standard (AES) and elliptic curve cryptography, can also be used to encrypt images~\cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed~\cite{murugan_survey_2018}.

 Using a homomorphic cryptosystem, operations can be performed on encrypted data while keeping both the operands and resulting values secure. The result of the operations can then be recovered when the data is decrypted. In this manner, data is manipulated without compromising data privacy~\cite{fontaine_survey_2007, sen_homomorphic_2013}. There is additional interest in being able to perform image manipulation operations on encrypted images such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}. More advanced operations have also been implemented using homomorphic cryptosystems, such as facial recognition \cite{hutchison_privacy-preserving_2009} and neural networks \cite{hesamifard_cryptodl:_2017}. While secure linear image operations have been implemented \cite{ziad_cryptoimg:_2016}, preprocessing which requires non-linear operations, such as certain methods of illumination processing \cite{oravec_illumination_2010}, has yet to be performed in the encrypted domain. This study in particular focuses on facial recognition.

### 2019-04-30 parts/01_introduction_05scopeandlimitations.tex
More revisions

\section{Scope and Limitations of the Study}
The study tests a fixed set of cryptosystems and image processing operations. 
We test the following algorithms:
\begin{enumerate}
	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
  \item The Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321}.
	\item The DGHV cryptosystem by Dijk, Gentry, Halevi, and Vaikuntanathan \cite{cryptoeprint:2009:616}, with optimizations from Coron, Naccache, and Tibouchi, \cite{cryptoeprint:2011:277, cryptoeprint:2011:440} to support shorter public keys.
	\item The Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
\end{enumerate}
We implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Non-linear intensity adjustment (logarithm, power-log transformations)
	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
\end{enumerate}
To test for image quality, we adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et. al~\cite{ahmed_benchmark_2016}. The presented benchmark uses many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	%\item Tests for preservation of image quality after encryption and decryption
	%\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
	%\end{enumerate}
	%\item Tests for cryptographic security
	%\begin{enumerate}
	%	\item Information entropy analysis
	%	\item Correlation coefficient analysis
	%	\item Differential analysis
  %      \begin{enumerate}
  %          \item Number of Pixel Change Rate (NPCR)
  %          \item Universal Average Change Intensity (UACI)
  %      \end{enumerate}
	%\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the methodology. Grayscale images will be used in the study.
A client-server model for secure computation will be assumed to allow operations such as secure comparison and exponentiation.
Training and test data are taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.

>>>>

\section{Scope and Limitations of the Study}
The study tests a fixed set of cryptosystems and image processing operations. 
We test the following algorithms:
\begin{enumerate}
	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
  \item The Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321}.
	\item The DGHV cryptosystem by Dijk, Gentry, Halevi, and Vaikuntanathan \cite{cryptoeprint:2009:616}, with optimizations from Coron, Naccache, and Tibouchi, \cite{cryptoeprint:2011:277, cryptoeprint:2011:440} to support shorter public keys.
	\item The Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
\end{enumerate}
We implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Non-linear intensity adjustment (logarithm, power-log transformations);
	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
\end{enumerate}
To test for image quality, we adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et. al~\cite{ahmed_benchmark_2016}. The presented benchmark uses many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	%\item Tests for preservation of image quality after encryption and decryption
	%\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
	%\end{enumerate}
	%\item Tests for cryptographic security
	%\begin{enumerate}
	%	\item Information entropy analysis
	%	\item Correlation coefficient analysis
	%	\item Differential analysis
  %      \begin{enumerate}
  %          \item Number of Pixel Change Rate (NPCR)
  %          \item Universal Average Change Intensity (UACI)
  %      \end{enumerate}
	%\end{enumerate}
\end{enumerate}
A detailed overview of the above is provided in the methodology. A client-server model for secure computation will be assumed to allow a larger range of secure operations. 
Grayscale images are used in the study. Training and test data taken from the publicly available \texttt{faces94} dataset (\url{https://cswww.essex.ac.uk/mv/allfaces/faces94.html}) maintained by the University of Essex.

### 2019-04-30 parts/02_relatedliterature.tex
More revisions

\section{Summary}
We have seen how privacy-preserving image operations have been implemented in the literature using partially homomorphic cryptosystems. \textit{CryptoImg} provided a suite of linear image processing operations using the Paillier cryptosystem, while Erkin, et al. have implemented a privacy-preserving version of the eigenfaces approach to facial recognition developed by Turk and Pentland.

We have presented as well several areas in which our study will expand on the research so far.
\begin{enumerate}
  \item We have shown two fully homomorphic cryptosystems, the DGHV cryptosystem and the BGV cryptosystem. While these cryptosystems are generally less efficient than partially homomorphic cryptosystems, they do not require additional protocols for division, multiplication, and exponentiation.
  \item Due to the general limitations of partially homomorphic systems, attempts at applying homomorphic cryptography to applications such as image processing and facial recognition have mainly been restricted to linear operations on ciphertext. We have shown that there are basic image processing operations which are non-linear, which can be approximated.
  \item While privacy-preserving facial recognition has been accomplished by Erkin, et al., privacy-preserving facial detection has yet to explored.
\end{enumerate}

>>>>

\section{Summary}
We have seen how privacy-preserving image operations have been implemented in the literature using partially homomorphic cryptosystems. \textit{CryptoImg} provided a suite of linear image processing operations using the Paillier cryptosystem, while Erkin, et al. have implemented a privacy-preserving facial recognition system using eigenfaces.

We have shown two fully homomorphic cryptosystems, the DGHV cryptosystem and the BGV cryptosystem. While these cryptosystems are generally less efficient than partially homomorphic cryptosystems, they do not require additional protocols for division, multiplication, and exponentiation. Due to the general limitations of partially homomorphic systems, attempts at applying homomorphic cryptography to applications such as image processing and facial recognition have mainly been restricted to linear operations on ciphertext. We have shown that there are basic image processing operations which are non-linear, which can be approximated.

Lastly, while privacy-preserving facial recognition has been accomplished by Erkin, et al., privacy-preserving facial detection has yet to explored.
\end{enumerate}

### 2019-04-30 parts/02_relatedliterature_02commonimageprocessingoperations.tex
More revisions

An image negation transformation is defined as:
\begin{equation}
    T\left(r\right) = L-1-r
\end{equation}
After applying image negation, the resulting image would be similar to a photographic negative~\cite{gonzalez_digital_2008}.

A brightness control transformation with parameter $v$ is defined as:
\begin{equation}
    T\left(r,v\right) = r+v
\end{equation}
The above transformations are linear in terms of the input $r$, and are thus simple to implement under a homomorphic cryptosystem.

>>>>

An image negation transformation is defined as
\begin{equation}
    T\left(r\right) = L-r
\end{equation}
where $L$ is the maximum pixel intensity value of an image.
After applying image negation, the resulting image would be similar to a photographic negative~\cite{gonzalez_digital_2008}.

A brightness control transformation with parameter $v$ is defined as
\begin{equation}
    T\left(r,v\right) = r+v.
\end{equation}
The above transformations are linear in terms of the input $r$, and are thus simple to implement under a homomorphic cryptosystem.

### 2019-04-30 parts/05_conclusions.tex
More revisions

Preliminary results have shown that both Paillier and DGK apply image negation accurately and efficiently, as evidenced by the perfect zero MSE and infinite PSNR. For the logarithm transformation, Paillier was faster and accurate enough (with $\text{MSE} \le 30$ and $\text{SSIM} \approx 0.99$) which was rather unexpected. However both Paillier and DGK fail to produce accurate results in applying the power-law transformation, with the latter failing to produce discernible results. Based from these results, the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.

@@

Future studies would involve improving and optimizing our implementation of non-linear intensity transformations in terms of number of operations, numerical accuracy and stability, and time efficiency.
% Future work would involve improving and optimizing our implementation of the DGK cryptosystem so that it performs faster.
% A suggestion would be to port the existing implementation to C/C++ and then create a Python library that acts as a wrapper to the C/C++ methods.
Furthermore, an implementation of a client-server framework or system dealing with secure image processing can be considered.

>>>>

Preliminary results have shown that both Paillier and DGK apply image negation accurately and efficiently, as evidenced by the perfect zero MSE and infinite PSNR. For the logarithm transformation, Paillier was faster and accurate enough (with $\text{MSE} \le 30$ and $\text{SSIM} \approx 0.99$) which was rather unexpected. However both Paillier and DGK fail to produce accurate results in applying the power-law transformation, with the latter failing to produce discernible results. Based on these results, the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.

@@

Future studies would involve improving and optimizing our implementation of non-linear intensity transformations in terms of number of operations, numerical accuracy and stability, and time efficiency.
% Future work would involve improving and optimizing our implementation of the DGK cryptosystem so that it performs faster.
% A suggestion would be to port the existing implementation to C/C++ and then create a Python library that acts as a wrapper to the C/C++ methods.
Furthermore, an implementation of a client-server system dealing with secure image processing can be considered.
